The Five Pillars of Translational Digital Medicine

### 2022-05-08 main.tex
waty's work

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{Steve Harris\,$^{1,2*}$, Tim Bonnici\,$^{1,2}$ Thomas Keen\,$^{1}$ Watjana Lilaonitkul\,$^{1}$ Nel Swanepoel\,$^{3}$ Mark White\,$^{4}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.

>>>>

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{Steve Harris\,$^{1,2*}$ Tim Bonnici\,$^{1,2}$ Thomas Keen\,$^{1}$ Watjana Lilaonitkul\,$^{1}$ Mark J White\,$^{4}$ Nel Swanepoel\,$^{3}$ }
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
